ECE 612, Information Theory

### 2024-04-11 information-theory/main.tex
Added divergence stuff; fixed typos

    \begin{definition}[Mutual informaiton]
    The mutual information between two random variables $X, Y$ is defined by

    \begin{equation*}
        I(X; Y) = H(X) - H(X \mid Y)
    \end{equation*}
    \end{definition}

>>>>

    \begin{definition}[KL Divergence]
        The \textbf{KL Divergence} between two probability distributions $p, q$ on the same support $\mathcal{X}$ is defined by

        \begin{equation*}
            D(p \Vert q) = \sum_{x \in \mathcal{X}} p(x) \log{
                \frac{p(x)}{q(x)}
            }
        \end{equation*}
    \end{definition}

    \begin{definition}[Mutual information]
        The mutual information between two random variables $X, Y$ is defined by

        \begin{equation*}
            I(X; Y) = H(X) - H(X \mid Y)
        \end{equation*}

        It can also be expressed as the KL divergence between the joint distribution $p_{X, Y}$ and the product of marginal distribution $p_Xp_Y$:

        \begin{equation*}
            I(X; Y) = D(p_{X,Y} \Vert p_X \cdot p_Y)
        \end{equation*}
    \end{definition}
